\section{House Rules}
To ensure that everybody is on the same page regarding for example the topics of meeting times and penalties, a set of house rules have been made. Everybody in this project group have thought about them and agreed to them. These house rules can be found below.

\begin{itemize}[noitemsep]
    \item The group members all come together on Mondays and Thursday from 8:45 till 12:30.
    \item There will be two meeting on those days, one at the start and one at the end of the session.
    \item If somebody is more than 5 minutes late without a good reason they will have to bring food for the whole group, this will be done at the next meeting.
    \item Every morning a break of 15 minutes is allowed.
    \item 24 hours before a deadline everything has to be finished, so team members have time to review it. 
    \item During meetings one person talks at a time.
\end{itemize}

\subsection{Planning}
A good time plan and division of the subsystems is very important, this is to make sure that the workload of this project is spread evenly in between the students and that there will be enough time to finish this project. The project has been divided into four modules, these modules can be found in Table \ref{tab:mod_div}.

The schedule that was shown in a presentation at the beginning of this project will be used as time plan \cite{Presentation}. As a group it has been decided that additional days might be necessary to ensure that the project can be finished with the best result possible, so additional meetings will be planned if it is deemed necessary.

\begin{table}[ht!]
    \centering
    \caption{Table with the module divisions.}
    \begin{tabular}{|l|r|}
    \hline
    Module                              & Students \\
    \hline
    Map generator \& Hitbox scanner     &  Michael, Talha and Daniel P.\\
    Coördinates                         & Ferdi and Hitesh\\
    Output (VGA + sound)                & Joris and Tim\\
    Bomb timer, Hit Register \& Victory & Koen and Daniel V.\\
     \hline
    \end{tabular}
    
    \label{tab:mod_div}
\end{table}